Longitudinal Principal Manifold Estimation

### 2023-11-10 paper/main.tex
update simulation table orientation

\begin{table}
\small
  \centering
  \begin{tabular}{|c c c c c|}
    \hline
    Case & $d$ & $D$ & $f_t(\mathbf{r})$ & Domain \\
    \hline
    1 & 1 & 2 & $\left(r, \ \alpha \text{sin} \ (\beta r + \frac{\pi}{2})\right) + \zeta\mathbf{g}(t) + \iota$ & $-3 \leq r \leq 3$ \\
    2 & 1 & 2 & $\left(r, \ \alpha\text{sin} \ (\beta r)\right) + \zeta\mathbf{g}(t) + \iota$ & $-3\pi \leq r \leq 3\pi$ \\
    3 & 1 & 2 & $\left(\alpha_1 \text{cos} \ (\beta_1 r), \ \alpha_2\text{cos} \ (\beta_2 r)\right) + \zeta\mathbf{g}(t) + \iota$ & $-\frac{4\pi}{5} \leq r \leq \frac{\pi}{2}$ \\
    4 & 1 & 3 & $\left(r, (\alpha_1r + \beta_1)^2, \ (\alpha_2r + \beta_2)^3\right) + \zeta\mathbf{g}(t) + \iota$ & $-1 \leq r \leq 1$ \\
    5 & 1 & 3 & $\left(r, \ \alpha_1\text{cos} \ (\beta_1 r), \ \alpha_2\text{sin} \ (\beta_2 r) \right) + \zeta\mathbf{g}(t) + \iota$ & $0 \leq r \leq 3\pi$ \\
    6 & 2 & 3 & $\left(\beta_1r_1, \ \beta_2r_2, \ \alpha_1(\alpha_2\|\beta\mathbf{r}\|^2)\right) + \zeta\mathbf{g}(t) + \iota$ & $-1 \leq r_1, r_2 \leq 1$\\
    7 & 2 & 3 & $\left(\alpha_1\beta_1r_1\text{cos} \ (\alpha_1r_1), \ \alpha_2\beta_2r_1\text{sin} \ (\alpha_2r_1), \ r_2\right) + \zeta\mathbf{g}(t) + \iota$ & $0 \leq r_1 \leq 3\pi$; \ $-1 \leq r_2 \leq 1$\\
    8 & 2 & 3 & $\left(\alpha_1\text{sin}(\beta_1r_1)\text{cos}(\beta_2r_2), \ \alpha_1\text{sin}(\beta_1r_1)\text{sin}(\beta_2r_2), \ \alpha_1\text{cos}(\beta_1r_1)\right) + \zeta\mathbf{g}(t) + \iota$ & $0 \leq r_1 \leq \pi$; \ $0 \leq r_2 \leq 2\pi$\\
    9 & 2 & 3 & $\left(\theta\text{sin} \ (\beta_1r_1)\text{cos} \ (\beta_2r_2), \ \theta\text{sin} \ (\beta_1)\text{sin} \ (\beta_2r_2), \ \theta\text{cos} \ (\beta_1r_1)\right) + \zeta\mathbf{g}(t) + \iota$ & $0 \leq r_1 \leq \pi$; \ $0 \leq r_2 \leq 2\pi$\\
    \hline
  \end{tabular}
  \caption{Embedding functions used for simulation trials.}
  \label{table:simulation_embeddings}
\end{table}

@@

\zielinski{It may be necessary to put some of the simulation figures in an appendix. Additionally, the figures are still very much a work in progress and are serving more of a placeholder status at the moment. Any suggestions regarding how to improve the clarity and depth perception of the figures would be greatly appreciated!}

\begin{table}[h]
\footnotesize
  \centering
  \begin{tabular}{|c c c c c c c c c c|}
    \hline
    Method & Case 1 & Case 2 & Case 3 & Case 4 & Case 5 & Case 6 & Case 7 & Case 8 \\
    \hline
    Data & 0.223 (0.256) & 0.514 (0.408) & 0.446 (0.445) & 30.7 (88.1) & 0.980 (0.771) & 1.43 (6.04) & 0.580 (0.839) & 0.226 (0.275) \\
    LPME & 0.125 (0.161) & 0.384 (0.648) & 0.401 (0.446) & 27.7 (260) & 0.791 (0.845) & 1.20 (5.66) & 4.07 (3.30) & 0.136 (0.169) \\
    PME & 0.268 (0.850) & 0.843 (1.93) & 0.507 (0.594) & 30.7 (88.2) & 1.04 (1.07) & 1.47 (6.06) & 7.37 (1.14) & 0.242 (0.311) \\
    PC/PS & 0.189 (0.245) & 0.600 (0.296) & 0.412 (0.423) & 30.6 (88.1) & 0.934 (0.713) & 1.01 (2.11) & 1.95 (0.800) & 0.274 (0.243) \\
    \hline
  \end{tabular}
  \caption{MSD Comparison to True Values, Mean (SD).}
  \label{table:simulation_results_mean}
\end{table}

\begin{table}[h]
\footnotesize
  \centering
  \begin{tabular}{|c c c c c c c c c c|}
    \hline
    Method & Case 1 & Case 2 & Case 3 & Case 4 & Case 5 & Case 6 & Case 7 & Case 8 \\
    \hline
    Data & 0.146 (0.233) & 0.467 (0.665) & 0.291 (0.601) & 4.26 (21.2) & 0.895 (1.33) & 0.284 (1.06) & 0.145 (0.552) & 0.110 (0.325) \\
    LPME & 0.074 (0.122) & 0.248 (0.461) & 0.239 (0.564) & 3.29 (13.0) & 0.584 (1.08) & 0.273 (0.891) & 2.96 (4.65) & 0.074 (0.208) \\
    PME & 0.131 (0.258) & 0.516 (0.750) & 0.317 (0.640) & 4.23 (21.1) & 0.894 (1.36) & 0.316 (1.04) & 6.92 (1.17) & 0.115 (0.331) \\
    PC/PS & 0.118 (0.206) & 0.564 (0.419) & 0.264 (0.584) & 4.22 (21.2) & 0.821 (1.22) & 0.557 (0.387) & 1.58 (0.514) & 0.172 (0.234) \\
    \hline
  \end{tabular}
  \caption{MSD Comparison to True Values, Median (IQR).}
  \label{table:simulation_results_median}
\end{table}

>>>>

\begin{table}
\small
  \centering
  \begin{tabular}{|c c c c c|}
    \hline
    Case & $d$ & $D$ & $f_t(\mathbf{r})$ & Domain \\
    \hline
    1 & 1 & 2 & $\left(r, \ \alpha \text{sin} \ (\beta r + \frac{\pi}{2})\right) + \zeta\mathbf{g}(t) + \iota$ & $-3 \leq r \leq 3$ \\
    2 & 1 & 2 & $\left(r, \ \alpha\text{sin} \ (\beta r)\right) + \zeta\mathbf{g}(t) + \iota$ & $-3\pi \leq r \leq 3\pi$ \\
    3 & 1 & 2 & $\left(\alpha_1 \text{cos} \ (\beta_1 r), \ \alpha_2\text{cos} \ (\beta_2 r)\right) + \zeta\mathbf{g}(t) + \iota$ & $-\frac{4\pi}{5} \leq r \leq \frac{\pi}{2}$ \\
    4 & 1 & 3 & $\left(r, (\alpha_1r + \beta_1)^2, \ (\alpha_2r + \beta_2)^3\right) + \zeta\mathbf{g}(t) + \iota$ & $-1 \leq r \leq 1$ \\
    5 & 1 & 3 & $\left(r, \ \alpha_1\text{cos} \ (\beta_1 r), \ \alpha_2\text{sin} \ (\beta_2 r) \right) + \zeta\mathbf{g}(t) + \iota$ & $0 \leq r \leq 3\pi$ \\
    6 & 2 & 3 & $\left(\beta_1r_1, \ \beta_2r_2, \ \alpha_1(\alpha_2\|\beta\mathbf{r}\|^2)\right) + \zeta\mathbf{g}(t) + \iota$ & $-1 \leq r_1, r_2 \leq 1$\\
    7 & 2 & 3 & $\left(\alpha_1\beta_1r_1\text{cos} \ (\alpha_1r_1), \ \alpha_2\beta_2r_1\text{sin} \ (\alpha_2r_1), \ r_2\right) + \zeta\mathbf{g}(t) + \iota$ & $0 \leq r_1 \leq 3\pi$; \ $-1 \leq r_2 \leq 1$\\
    8 & 2 & 3 & $\left(\alpha_1\text{sin}(\beta_1r_1)\text{cos}(\beta_2r_2), \ \alpha_1\text{sin}(\beta_1r_1)\text{sin}(\beta_2r_2), \ \alpha_1\text{cos}(\beta_1r_1)\right) + \zeta\mathbf{g}(t) + \iota$ & $0 \leq r_1 \leq \pi$; \ $0 \leq r_2 \leq 2\pi$\\
    \hline
  \end{tabular}
  \caption{Embedding functions used for simulation trials.}
  \label{table:simulation_embeddings}
\end{table}

@@

\begin{table}[h]
  \centering
  \begin{tabular}{|c c c c c|}
    \hline
    Case & Data & LPME & PME & PC/PS \\
    \hline
    1 & 0.223 (0.256) & 0.125 (0.161) & 0.268 (0.850) & 0.189 (0.245) \\
    2 & 0.514 (0.408) & 0.384 (0.648) & 0.843 (1.93) & 0.600 (0.296) \\
    3 & 0.446 (0.445) & 0.401 (0.446) & 0.507 (0.594) & 0.412 (0.423) \\
    4 & 30.7 (88.1) & 27.7 (260) & 30.7 (88.2) & 30.6 (88.1) \\
    5 & 0.980 (0.771) & 0.791 (0.845) & 1.04 (1.07) & 0.934 (0.713) \\
    6 & 1.43 (6.04) & 1.21 (5.66) & 1.47 (6.06) & 1.01 (2.11) \\
    7 & 0.580 (0.839) & 4.07 (3.30) & 7.37 (1.14) & 1.95 (0.800) \\
    8 & 0.226 (0.275) & 0.136 (0.169) & 0.242 (0.311) & 0.274 (0.243) \\
    \hline
  \end{tabular}
  \caption{MSD Comparison to True Values, Mean (SD).}
  \label{table:simulation_results_mean}
\end{table}

\begin{table}[h]
  \centering
  \begin{tabular}{|c c c c c|}
    \hline
    Case & Data & LPME & PME & PC/PS \\
    \hline
    1 & 0.146 (0.233) & 0.074 (0.122) & 0.131 (0.258) & 0.118 (0.206) \\
    2 & 0.467 (0.665) & 0.248 (0.516) & 0.516 (0.750) & 0.564 (0.419) \\
    3 & 0.291 (0.601) & 0.239 (0.564) & 0.317 (0.640) & 0.264 (0.584) \\
    4 & 4.26 (21.2) & 3.29 (13.0) & 4.23 (21.1) & 4.22 (21.2) \\
    5 & 0.895 (1.33) & 0.584 (1.08) & 0.894 (1.36) & 0.821 (1.22) \\
    6 & 0.284 (1.06) & 0.273 (0.891) & 0.316 (1.04) & 0.557 (0.387) \\
    7 & 0.145 (0.552) & 2.96 (4.65) & 6.92 (1.17) & 1.58 (0.514) \\
    8 & 0.110 (0.325) & 0.074 (0.208) & 0.115 (0.331) & 0.172 (0.234) \\
    \hline
  \end{tabular}
  \caption{MSD Comparison to True Values, Median (IQR).}
  \label{table:simulation_results_median}
\end{table}
